Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-20 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
analogy section edited

\begin{figure}[t!]
  \includegraphics[width=\columnwidth]{images/classroom-peekabot-annotated.pdf}
  \caption{A visualization of Dora's existing spatial model taken from the running system. Walls are visualized where flat surfaces (walls, desks and other objects) are detected during SLAM.}
  \label{fig:dora-spatial}
\end{figure}

@@

\textbf{TODO: Need to update example, including new fns, when we have updated pictures in.}

@@

% In the next section, we describe how to transfer these environment-specific representations to new situations via analogy.

@@

% While this work focuses on how analogy enables inferences from specific examples to new situations, but its role in the larger cognitive system this work envisions cannot be ignored.

We assume that a cognitive system will have a way of initially acquiring examples of context-dependent spatial regions, e.g., by being taught by a human through dialogue, sketching, or hand-coding. As stated previously, to avoid burdening potential tutors with the task of teaching the system every context-dependent spatial region individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after its initial training. For example, after training a janitorial robot in just one classroom, it should be able to identify similar regions in the other classrooms in the building. Motivated by the learning and generalization abilities of humans, we have chosen analogy to tackle this problem.

@@

The Structure-Mapping Engine (SME) \cite{Falkenhainer1989a} performs analogical matching. Given two structured representations as input (the base and target), SME produces one or more mappings. Each mapping is represented by a set of \textit{correspondences} between entities and expressions in the base and target.  Mappings also include \textit{candidate inferences} which are conjectures about the target using expressions from the base which, while unmapped in their entirety, have subcomponents that participate in the mapping's correspondences. SME operates in polynomial time, using a greedy algorithm \cite{Forbus/etal1994}.

@@

@@

In our system, the base and target representations consist of the identified objects from Dora's spatial model drawn from two different runs in two different environment, plus the qualitative spatial relationships computed on top of these. The base also contains a labeled context-dependent spatial region that is sought in target environment. We use SME to create an analogical mapping between the base and target. The result of this mapping is a set of correspondences and a set of candidate inferences. We transfer context-dependent spatial regions as follows. First, we identify the context-dependent spatial region entity of the sought semantic type in the base. This entity should not participate in the mapping, but should be included as \fw{:skolem} expressions in the candidate inferences. To transfer this entity to the target, we collect the candidate inferences resulting from the \fw{regionBoundary} statements in the base that mention the base entity. The second arguments of these candidate inferences are anchor points in the target environment. Therefore, to identify the context-dependent spatial region in the target, we create a new entity, assign it the semantic type of the sought region, and define its boundary using the anchor points from the candidate inferences.

>>>>

@@

\from{Nick}{TODO: Need to update example, including new fns, when we have updated pictures in.}

@@

@@

We assume that a cognitive system will have a way of initially acquiring examples of CDSRs, e.g., by being taught through dialogue, sketching, or hand-coding. To avoid burdening potential tutors with the task of teaching the system every CDSR individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after initial training. For example, after a janitorial robot has been taught where the front of one classroom is, it should be able to identify the fronts of other classrooms in the building. Motivated by the learning and generalization abilities of humans, we have chosen \emph{analogy} as the approach our system will use to solve this problem.

@@

We use the Structure-Mapping Engine (SME) \cite{Falkenhainer1989a} to perform analogical matching in our system. Given two structured representations as input (the base and target), SME produces one or more mappings. Each mapping is represented by a set of \textit{correspondences} between entities and expressions in the base and target.  Mappings also include \textit{candidate inferences} which are conjectures about the target using expressions from the base which, while unmapped in their entirety, have subcomponents that participate in the mapping's correspondences. SME operates in polynomial time, using a greedy algorithm \cite{Forbus/etal1994}.

@@

\from{Nick}{TODO: Update Figure \ref{fig:analogy} with correct representation for current version.}

@@

In our system, the base and target representations consist of the entities Dora has perceived in two different rooms, plus the QSRs computed on top of these. The base also contains a labeled CDSR which we assume is sought in target. The result of result of running SME on these representations is a set of correspondences between the base and target, and a set of candidate inferences about the target. We use these to transfer the CDSR from base to target (i.e. recognizing the CDSR in the target) as follows. First, we identify the CDSR of the sought type in the base. This entity should not participate in the mapping, but should be included in \fw{:skolem} expressions in the candidate inferences. To transfer the CDSR to the target, we collect the candidate inferences that result from \fw{regionBoundary} statements mentioning the base CDSR. The second arguments of these candidate inferences are anchor points in the target environment. We use these to define the boundary of the CDSR in the target, linking them to a new CDSR entity using \fw{regionBoundary} statements.

### 2012-01-20 code/scenarios/cdsr/trunk/papers/AAAI2012/qsr-extraction.tex
analogy section edited

Given data from Dora's spatial model we compute a set of spatial relations between each pair of adjacent objects. For each object in the room we compute 8 spatial relations between that object and each of the objects adjacent to it; adjacency is determined by creating a voronoi diagram as is standard geometric reasoning \cite{Forbus/etal2003}. The relations we compute between a given object and one of the objects adjacent to it are analogous to the cardinal and intermediate points on the compass when the compass is centered on the object. The canonical directions of these relations are defined using the following vectors: $<0,1>$, $<1,1>$, $<1,0>$, $<1,-1>$, $<0,-1>$, $<-1,-1>$, $<-1,0>$, $<-1,1>$.

To compute these relations we first, extract the object and room entities from the sensor data. Next, for the room, we compute its region as a convex hull. Taking each object in the room in turn to be the current landmark, we translate the origin of the room to the landmark's centroid. This translation results in the coordinates of the all the other objects in the room being translated into a frame of references whose origin is the centroid of the landmark.  For each object adjacent to the landmark we compute the 8 relations by computing the inner angle between the vector from the origin (the landmark's centroid) and the object's location and the direction vector of the relation, as defined above. This angle is computed by taking the dot product of these two vectors. $\dots$

>>>>

\from{Nick}{Do these 8 relations have names? We need them here so we can refer to the predicates later.}

For each object that Dora detects we compute 8 spatial relations between that object and each of the objects adjacent to it; adjacency is determined using a voronoi diagram, as is standard in geometric reasoning \cite{Forbus/etal2003}. The relations we compute between each given \emph{landmark} object and its adjacent neighbour are analogous to the cardinal and intermediate points on the compass when the compass is centered on the object. The canonical directions of these relations are defined using the following vectors: $<0,1>$, $<1,1>$, $<1,0>$, $<1,-1>$, $<0,-1>$, $<-1,-1>$, $<-1,0>$, $<-1,1>$.

We generate these relations as follows. Taking each object in the room in turn to be the current landmark, we translate the origin of the room to the landmark's centroid. This results in the coordinates of the all the other objects in the room being translated into a frame of reference whose origin is the centroid of the landmark.  For each neighbour object adjacent to the landmark we compute the 8 relations by calculating the inner angle between the vector from the origin (the landmark's centroid) and the neighbour's location and the direction vector of the relation, as defined above. This angle is computed by taking the dot product of these two vectors. $\dots$
